TreehopperFitness: Run this file for all stats, tables, and figures

### 2023-08-30 manuscript/Manuscript_runfile.Rmd
Section 1 of manuscript runfile

# 0 - Data import

@@

>>>>

**Setup**

@@

# 1 - Maternal egg guarding increases offspring survivorship, and ants enhance this effect

## Prep

```{r}
## Load data
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
```

```{r}
## Fit models
# hatching success
des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ant_treatment")

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

surv_model_fits <- list(
  hatch = des_hatch.desL.ant_treatment.quad$fits,
  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
  Esurv = des_Esurv.desL.ant_treatment.quad$fits
)
```

## Figure 5

```{r}
(desL.ant_treatment.quad.p <- egg::ggarrange(
  des_hatch.desL.ant_treatment.quad$p +
    ylab("Hatching success") +
    theme(legend.position="none"),
  des_Nsurv.desL.ant_treatment.quad$p +
    ylab("Nymph survivorship") +
    theme(legend.position="none"),
  des_Esurv.desL.ant_treatment.quad$p +
    theme(legend.position = c(0.8,0.95)) + 
    ylab("Egg survivorship") +
    ylim(0,1),
  labels=c("A","B","C"),
  ncol=3))

ggsave(here("manuscript/",
            "Figure5.png"),
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Table 1

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desL.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ant_treatment.quad.qb.tbl, 
                Nsurv.desL.ant_treatment.quad.qb.tbl, 
                Esurv.desL.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("manuscript",
                                    "Table1.docx"))

```

## [Text] Hatching success

```{r}
## Sample size table
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())
```

```{r}
## Hatch
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_hatch.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_hatch.desL.ant_treatment.quad$fits$mai.qb)
```

# 2 - Offspring survivorship is equivalent when either mothers or ants guard nymphs

## [Text] Nymph survivorship

```{r}
# Nsurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
```

## [Text] Egg survivorship

```{r}
# Esurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Esurv.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
```

# 3 - Mothers dynamically adjust care depending on the presence of ants and conspecific females

## Figure Figure S3

## Figure 3

## [Text]

# 4 - Early visits by other females lead to early desertion of clutches

## Appendix A (?)

## Figure 4

## [Text]

# 5 - Ant mutualists reliably enhance lifetime fitness, but offloading care to peers is risky

## Figure 6

## Figure S4

## [Text]

# Old:
